The effect of linking assumptions and number of response options on inferred scalar implicature rate

### 2018-05-08 writeup.Rmd
inline edits to results section

In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)). However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time. That is, both under the weak and the strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.

@@

In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)). And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time. On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time. This means that the weak and strong link lead to different conclusions about implicature rates on the ternary task. Under the weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link it is only `r round(ternaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.

@@

In the quaternary task (Figure \@ref(fig:quaternaryPlot)), participants were again at or close to ceiling in responding 'right' and 'wrong' on 4 of the 6 unambiguously true and false trials. However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right". This suggests that perhaps participants considered a notion of partially true or correct statement in our experimental setting. Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.

@@

Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link. Under the weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.

@@

Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of  responses in the quinary task. Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively. The 2 control conditions that the quaternary task had revealed pragmatic infelicity in again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, requires fine-grained enough response options to be detected experimentally.

@@

Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link. Under the weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%.

<!--
In four trial types, participants provided the same responses regardless of how many response options were made available. The first two trial types include the guesses with an animal not on the card at all. In such trials, whether there was one or two animals on the card, participants considered the guess wrong. In the third and the fourth trial types, the gueses matched the aimal(s) on the card; if there was one animal on the card, that animal was mentioned and if there were two, both were mentioned using a conjunction. The fact that participants chose the extreme ends of the scale for these trial types and the responses did not change when intermediate options were provided suggests that participant judgments truly aligned with the opposite ends of the scale in these trial types.

>>>>

In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)). However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog) **bw: "(i.e. a "cat" or "cat or dog" description for a card with both a cat and a dog)"**, we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time. That is, both under the weak and the strong link **bw: Weak and Strong link assumptions (capitalization consistency with intro)** assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.

@@

In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)). And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog) **bw: "(a "cat" and "cat or dog" description for a card with both a cat and a dog)"**, we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time. On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time. This means that the weak and strong link **bw: Weak and Strong link** lead to different conclusions about implicature rates on the ternary task. Under the weak link **bw: Weak link**, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(ternaryExh_wrong$proportion*100)`%. Similarly, under the weak link **bw: Weak link**, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(ternaryScalar_wrong$proportion*100)`%.

@@

In the quaternary task (Figure \@ref(fig:quaternaryPlot)), participants were again at or close to ceiling in responding 'right' and 'wrong' on 4 of the 6 unambiguously true and false trials. However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right". This suggests that perhaps participants considered a notion of partially true or correct statement **bw: considered the notion of a partially true or correct statement** in our experimental setting. Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.

@@

Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link. Under the weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%. **bw: capitalize "Weak" and "Strong" in this paragraph**

@@

Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of responses in the quinary task. Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively. The 2 control conditions that the quaternary task had revealed pragmatic infelicity in **bw: The 2 control conditions in which the quaternary task had revealed pragmatic infelicity ** again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, **bw: "nonetheless" rather than "however"?** requires fine-grained enough response options to be detected experimentally.

@@

Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link **bw: Weak link or the Strong link**. Under the weak link **bw: Weak link**, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(quinaryExh_wrong$proportion*100)`%. Similarly, under the weak link **bw: Weak link**, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(quinaryScalar_wrong$proportion*100)`%. 
<!--
In four trial types, participants provided the same responses regardless of how many response options were made available. The first two trial types include the guesses with an animal not on the card at all. In such trials, whether there was one or two animals on the card, participants considered the guess wrong. In the third and the fourth trial types, the gueses matched the aimal(s) on the card; if there was one animal on the card, that animal was mentioned and if there were two, both were mentioned using a conjunction. The fact that participants chose the extreme ends of the scale for these trial types and the responses did not change when intermediate options were provided suggests that participant judgments truly aligned with the opposite ends of the scale in these trial types.
